---
title: "ESTC: `r params$place` docs (`r params$document.type`) in `r params$language` language `r params$min.year`-`r params$max.year`"
subtitle: "`r paste(params$subtitle)`"
author: "Mikko Tolonen, Leo Lahti, Eetu Makela et al."
date: "`r Sys.Date()`"
fontsize: 11pt
geometry: margin=1in
linkcolor: magenta
urlcolor: blue
citecolor: black
institute: "Universities of Helsinki & Turku"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
  pdf_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: header.tex
params:
  min.year: 
    label: "Start year:"
    input: numeric
    value: 1470
  max.year: 
    label: "End year:"
    input: numeric
    value: 1880
  time.window: 
    label: "Time window:"
    input: numeric
    value: 10
  date: 
    label: "Date:"
    value: !r date()
    input: date
  place: 
    label: "Publication place:"
    value: "All"
    choices: !r c("All", "London", "Edinburgh", "Dublin", "Boston Ma", "Philadelphia Pa", "Oxford", "Glasgow", "New York NY", "Cambridge", "Newcastle")
    input: select
  language:
    label: "Language: "
    value: "any"
    choices: !r c("any", "English", "Latin",  "French", "German", "Welsh")  
    input: select
  document.type:
    label: "Document type: "
    value: "All"
    choices: !r c("All", "Books", "Pamphlets")
    input: select    
  subtitle: 
    label: "Subtitle:"
    value: My subtitle
    input: text
  idsource: 
    label: "Document IDs:"
    value: data/history_of_england_headings.txt
    input: text
  update.bibliographica: 
    label: "Update bibliographica"
    value: FALSE
    input: checkbox
---


```{r init, message=TRUE, warning=TRUE, echo=TRUE, cache=FALSE}
# For all parameter options for rmarkdown slide rendering, see:
# http://rmarkdown.rstudio.com/developer_parameterized_reports.html
# More header options in Pandoc manual
# http://pandoc.org/MANUAL.html#templates

if (params$update.bibliographica) {
  library(devtools)
  install_github("ropengov/bibliographica")
}

# Read parameters from the header
# mydate <- params$start # not used -vv
min.year <- params$min.year
max.year <- params$max.year
selected.place <- params$place
time.window <- params$time.window
selected_language <- params$language
selected_document_type <- params$document.type
idsource <- params$idsource

# Limit the length of names to print on screen / figures
nchar <- 40
# Default number of top hits to show
ntop <- 20

library(devtools)
load_all("../../R/bibliographica")
library(bibliographica)
# load_all("R/estc")
load_all()
library(estc)
library(magrittr)
library(reshape2)
library(gridExtra)
library(knitr)
library(ggmap)
#library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(sorvi)
# source("R/rmdshiny_report_plot_functions.R")
# source("R/rmdshiny_setup_functions.R")
# source("R/rmdshiny_get_subset.R")
# source("R/rmdshiny_get_custom_ids.R")
# source("R/rmdshiny_query_summary_functions.R")
# source("R/rmdshiny_get_top_authors.R")
# source("R/rmdshiny_get_top_titles.R")
# source("R/rmdshiny_get_top_publishers.R")

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(fig.path = "figure_slides/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "figure_slides/")

# Set locale
# tmp <- Sys.setlocale(locale="UTF-8") 

# Nice theme
theme_set(theme_bw(26))

# Nice default themes
# https://github.com/cttobin/ggthemr#palettes
#ggthemr('fresh', text_size = 20)
# ggthemr('greyscale', text_size = 20)
#ggthemr('light', text_size = 20)
# ggthemr('pale', text_size = 20)
#ggthemr_reset() # Reset theme

```


```{r data, echo=TRUE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
## SELECT AND AUGMENT THE COMPLETE DATA SET (df.orig)

# Read the preprocessed data
df.orig <- readRDS("data/estc_df.Rds") # Keep the complete data

# Add Metadata ID field 
df.orig <- add_metadata_id_field(df.orig)

# Add document type
df.orig <- add_document_type(df.orig)

# Set the desired time window (default one decade)
df.orig <- set_time_window(df.orig, time.window)

# --------------------------------------

## PICK SELECTED SUBSET OF THE DATA (df.preprocessed AND df.preprocessed.allplaces)

# # Now pick selected subset (time, place, language..)
data_subset <- get_subset(df.orig,
                          min.year,
                          max.year,
                          selected_language,
                          selected_document_type,
                          selected.place)

df.preprocessed           <- data_subset$place_subsetted
df.preprocessed.allplaces <- data_subset$all_places

# ---------------------------------------

## PICK SELECTED DOCUMENTS (df0)

# # Read the custom list of entry IDs
# # Including also the number of hits per document
# # and document total length for normalization purposes
custom.ids <- get_custom_ids(data_subset$place_subsetted, idsource)

# #---------------------------------------------------------
# 
# # Pick entries with the given IDs.. must remove the source ID from the ESTC strings

df0 <- subset(df.preprocessed, id %in% custom.ids$id)
# Selected place
# Keep also version with all places
df0.allplaces <- subset(df.preprocessed.allplaces, id %in% custom.ids$id)  

# Not found
# notfound <- setdiff(custom.ids$id, df0$id)
notfound <- get_ids_not_found(custom.ids, df0)

# Combine duplicated customIDs
# custom.ids <- custom.ids %>% group_by(id) %>%
# 	                     summarise(freq = sum(freq, na.rm = T),
# 	                     	       length = sum(length, na.rm = T)
# 			     )
custom.ids <- combine_duplicated_query_ids(custom.ids)

# # Add normalization field: hits per 1000 words
# custom.ids$freq.normalized <- 1e3 * custom.ids$freq/custom.ids$length
custom.ids <- add_normalization_field(custom.ids)

# # Number and percentage of the custom list IDs that were found
# # in the very original data
# hitn0 <- sum(custom.ids$id %in% df.orig$id, na.rm = TRUE)
# hitp0 <- 100 * hitn0/nrow(custom.ids)
query_hits_in_data_original <- get_query_hits_amount(custom.ids, df.orig)
hitn0 <- query_hits_in_data_original$hits_amount
hitp0 <- query_hits_in_data_original$percentile

# # Hits after final subsetting
query_hits_in_data_subset <-  get_query_hits_amount(custom.ids, df0)
hitn1 <- query_hits_in_data_subset$hits_amount
hitp1 <- query_hits_in_data_subset$percentile

# Duplicated entries
duplicated.ids.in.estc  <- get_sum_duplicate_ids(df.preprocessed$id)
# !NOTE does this ever return something else than 0? Duplicates removed earlier -vv
duplicated.ids.in.query <- get_sum_duplicate_ids(custom.ids$id)
```

### Technical notes

Selected place: `r params$place`

Selected language: `r params$language`

Document format: `r params$document.type`

Query IDs (n=`r nrow(custom.ids)`) from file:  `r params$idsource`  

IDs found from complete ESTC: n=`r hitn0` (`r round(hitp0, 2)` %)  

IDs found after subsetting (time, place, language, document type): n=`r hitn1` (`r round(hitp1, 2)` %)   

Duplicated IDs in ESTC: n = `r duplicated.ids.in.estc` (`r round(100 * duplicated.ids.in.estc/nrow(df.preprocessed), 1)`%). Very few, each occurrence is considered separately.  

Duplicated IDs in the query: `r duplicated.ids.in.query` (`r round(100 * duplicated.ids.in.query/nrow(custom.ids), 1)`%). According to a single check, these are often series with same ID over many issues. The total sum of query hits and lengths is used.  


```{r normalization, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=7, fig.height=7, out.width="100px", eval=FALSE}
# Document length vs. normalized hit frequency:
p <- ggplot(custom.ids, aes(x = length, y = freq.normalized)) + 
       geom_point() + scale_x_log10() + scale_y_log10() +
       xlab("Document length") + ylab("Hits per unit length (x1000)")
print(p)       
```


### Timeline for title count

Left: self-explanatory; Right: fraction of the ECCO query compared to all selected documents (time, language). If a specific place is selected, two bars are shown: one for the selected place and one for all places.

```{r titlecount, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.width=15, fig.height=7}
# # If selected place is given, then show
# # both the selected and all places
titlecount_plot <- plot_titlecount_timeline(df0, df0.allplaces, selected.place)

# # Compare the selected field in between the two data sets
relative_titlecount_plot <-
  plot_relative_titlecount_timeline(df0, df0.allplaces, df.preprocessed,
                                    df.preprocessed.allplaces,
                                    selected.place)

grid.arrange(titlecount_plot, relative_titlecount_plot, nrow = 1)
```


### Timeline for paper consumption

Left: self-explanatory; Right: fraction of the ECCO query compared to all selected documents (time, language). If a specific place is selected, two bars are shown: one for the selected place and one for all places.

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.width=15, fig.height=7}
# # If selected place is given, then show
# # both the selected and all places
paper_consumption_plot <- plot_paper_consumption_timeline(df0,
                                                          df0.allplaces,
                                                          selected.place)

# # Compare the selected field in between the two data sets
relative_paper_consumption_plot <-
  plot_relative_paper_consumption_timeline(df0,
                                           df0.allplaces,
                                           df.preprocessed,
                                           df.preprocessed.allplaces,
                                           selected.place,
                                           myfield = "paper")

grid.arrange(paper_consumption_plot, relative_paper_consumption_plot, nrow = 1)
```


### Paper consumption: books vs. pamphlets

This figure is shown only when document.type "All" is selected.

```{r bookvspamphlets, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=7}
if (params$document.type == "All") {
  books_vs_pamphlets_plot <- plot_books_vs_pamphlets(df0)
  print(books_vs_pamphlets_plot)
} 
```


### Top authors

The top authors by title count (left; total hits across all editions
shown in the middle); or by hits per edition (right)

```{r topauthors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}

hits_per_author_all <- get_hits_per_author(df0, custom.ids, field = "author", nchar = nchar)
top_authors_by_hits <- get_top_authors(hits_per_author_all, ntop)
top_authors_by_edition <- get_top_authors_by_edition(hits_per_author_all)
# dfs <- hits_per_author_top_n

theme_set(theme_bw(15))  

top_authors_total_hits_plot <- plot_top_authors_total_hits(top_authors_by_hits)
top_authors_hits_per_edition_plot <-
  plot_top_authors_hits_per_edition(top_authors_by_hits)
top_authors_hits_per_edition_arranged_plot <-
  plot_top_authors_hits_per_edition(top_authors_by_edition)

grid.arrange(top_authors_total_hits_plot,
             top_authors_hits_per_edition_plot,
             top_authors_hits_per_edition_arranged_plot,
             nrow = 1)
```


### Title count timeline for top 10 authors

```{r topauthorstimeline, fig.height=4, fig.width=10, echo=FALSE}
plot_titlecount_top10_authors <-
  plot_titlecount_timeline_for_top10_authors(df0)

print(plot_titlecount_top10_authors)
```


### Top places

The top places defined by title count (left); Relation between
titlecount and query hits (right). Note that document lengths are not
taken into account here.

```{r topplaces, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}
plot_top_places_by_titlecount <- top_places_by_titlecount_plot(df0, ntop)
plot_titlecount_queryhits <- titlecount_queryhits_relation_plot(df0, custom.ids,
                                                                field = "publication_place")

grid.arrange(plot_top_places_by_titlecount,
             plot_titlecount_queryhits,
             nrow = 1)
```


### Top titles by title count

Up to `r nchar` first characters for each title are shown.

```{r toptitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}
toptitles <- plot_top_titles_by_title_count(df0, nchar)
print(toptitles)
```


### Top hits/title

The title length is limited up to `r nchar` first characters:

```{r toptitles2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}

total_titlehits <- get_total_titlehits(df0, custom.ids, nchar = nchar)
top10_titles <- get_top_n_titles(total_titlehits, ntop = ntop, custom.ids = custom.ids)
top_titles_by_edition <- get_top_titles_by_edition(total_titlehits, ntop)

theme_set(theme_bw(15))  

plot_top_titlehits <- top_titlehits_plot(top10_titles)
plot_top_titlehits_edition <- top_titlehits_edition_plot(top10_titles)
plot_top_titlehits_edition_by_edition <-
  top_titlehits_edition_plot(top_titles_by_edition)

grid.arrange(plot_top_titlehits,
             plot_top_titlehits_edition,
             plot_top_titlehits_edition_by_edition,
             nrow = 1)
```


### Top publishers

The top publishers can be defined by title count (left) or by the total hits
across all documents (right).

```{r toppublishers, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}

top_publishers_abs_hits <- get_top_publishers_abs_hits(df0, custom.ids,
                                                       field = "publisher",
                                                       ntop = ntop, nchar = nchar)
  
theme_set(theme_bw(15))

plot_top_publishers <- top_publishers_plot(df0,
                                           ntop = ntop,
                                           nchar = nchar)
plot_top_publishers_abs_hits <-
  top_publishers_abs_hits_plot(top_publishers_abs_hits)
  
grid.arrange(plot_top_publishers,
             plot_top_publishers_abs_hits,
             nrow = 1)
```

